Think deep for reef resilience

### 2025-08-14 paper/paper_draft.qmd
Update .qmd file to respect new figures directory

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points). Colour-coded areas outline GBR marine park management regions,
where orange represents the Far Northern management region, green represents
Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
[@GBRMPA2007]. Reef centroids are marked individually for visual clarity, and are coloured
according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
represented in this figure. An annotation represents the approximate location of the
Australian Institute of Marine Science Townsville site at Cape
Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
fig-align="center" width="14.8cm"}

@@

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 95th percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
fig-align="center" width="14.82cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025
to 1. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Displays results from median timeseries using
ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
fig-align="center" width="14.82cm"}

@@

![Reef area-relative coral cover timeseries clustered within each management area, for each
GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 95th percentile confidence intervals. Each management area is represented five
times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
fig-align="center" width="14.82cm"}

@@

![Median depth for reefs within each bioregion, separated into clusters assigned by
timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
are clusters with intermediate median area-relative cover between 2030 and 2040 within each
bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
fig-align="center" width="14.82cm"}

@@

![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
fig-align="center" width="10cm"}

![Distribution of depth data coverage levels across 3806 possible reefs. Reefs below the 5%
data coverage threshold (represented by the red vertical line) were removed from the
investigation.](../outputs/ADRIA_results/HighResCoralStress/figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
fig-align="center" width="14.8cm" height="9.5cm"}

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
represented five times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by management area scale cluster assignment.
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Reefs that do not have a consistent cluster
assignment level across all GCMs at mangement area scale are gray. All consistently
clustered reefs are coloured according to their management area scale cluster assignment.
Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
investigation are represented in this figure. An annotation represents the approximate
location of the Australian Institute of Marine Science Townsville site at Cape
Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
fig-align="center" width="14.82cm"}

![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
Green indicates a low cover cluster assignment, orange represents a medium cover assignment
and blue represents assignment of a reef to a high coral cover cluster. The vertical width
of reef elements varies depending on the number of reefs within the bioregion (displayed in
the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
ACCESS-CM2, NorESM2-MM and
GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
fig-align="center" width="14.82cm"}

![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef
connectivity relative standard deviation represents the reef standard deviation connection
strength as a percentage of reef mean connection strength. Lighter colours indicate higher
RSD %
values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
fig-align="center" width="14.82cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
total connectivity strength and the number of years cover exceeds the carbonate budget
threshold. Colour of each point represents the base-10 log of scaled reef total connectivity
strength. Displays results from median timeseries using
ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
fig-align="center" width="14.82cm"}

@@

![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
clusters with the highest median area-relative cover between 2030 and 2040 within each
bioregion. Solid lines represent the cluster median timeseries and bands represent the 95th
percentile confidence intervals. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
fig-align="center" width="14.82cm"}

![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines represent the median cover – DHW correlation level for each cluster. Displays results
for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
fig-align="center" width="14.82cm"}

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW level for each cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
fig-align="center" width="14.82cm"}

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
fig-align="center" width="14.82cm"}

![Initial proportion of coral habitable area occupied by corals for reefs within each
bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
are clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines represent the median proportion of habitable area occupied for each cluster. Displays
results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
fig-align="center" width="14.82cm"}

![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines within each violin represent the median source-to-sink ratio for each cluster and grey
points represent the ratio value for each reef. Vertical grey lines represent a
source-to-sink ratio of 0 (in base-10 log scale) indicating equal outgoing and incoming
connectivity levels. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
fig-align="center" width="14.82cm"}

![Total connectivity strength (in base-10 log scale) for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines within each violin represent the median base-10 log of total connectivity strength for
each cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
fig-align="center" width="14.82cm"}

>>>>

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points). Colour-coded areas outline GBR marine park management regions,
where orange represents the Far Northern management region, green represents
Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
[@GBRMPA2007]. Reef centroids are marked individually for visual clarity, and are coloured
according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
represented in this figure. An annotation represents the approximate location of the
Australian Institute of Marine Science Townsville site at Cape
Cleveland.](../figs/region_map.png){#fig-region-map
fig-align="center" width="14.8cm"}

@@

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 95th percentile confidence
intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws
fig-align="center" width="14.82cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025
to 1. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Displays results from median timeseries using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
fig-align="center" width="14.82cm"}

@@

![Reef area-relative coral cover timeseries clustered within each management area, for each
GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 95th percentile confidence intervals. Each management area is represented five
times (for each GCM), with each GCM displayed
horizontally.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
fig-align="center" width="14.82cm"}

@@

![Median depth for reefs within each bioregion, separated into clusters assigned by
timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
are clusters with intermediate median area-relative cover between 2030 and 2040 within each
bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
cluster. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
fig-align="center" width="14.82cm"}

@@

![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
2021).](../figs/ecs_plot.png){#sfig-ecs
fig-align="center" width="10cm"}

![Distribution of depth data coverage levels across 3806 possible reefs. Reefs below the 5%
data coverage threshold (represented by the red vertical line) were removed from the
investigation.](../figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
fig-align="center" width="14.8cm" height="9.5cm"}

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
represented five times (for each GCM), with each GCM displayed
horizontally.](../figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by management area scale cluster assignment.
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Reefs that do not have a consistent cluster
assignment level across all GCMs at mangement area scale are gray. All consistently
clustered reefs are coloured according to their management area scale cluster assignment.
Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
investigation are represented in this figure. An annotation represents the approximate
location of the Australian Institute of Marine Science Townsville site at Cape
Cleveland.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
fig-align="center" width="14.82cm"}

![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
Green indicates a low cover cluster assignment, orange represents a medium cover assignment
and blue represents assignment of a reef to a high coral cover cluster. The vertical width
of reef elements varies depending on the number of reefs within the bioregion (displayed in
the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
ACCESS-CM2, NorESM2-MM and
GFDL-CM4).](../figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
fig-align="center" width="14.82cm"}

![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef
connectivity relative standard deviation represents the reef standard deviation connection
strength as a percentage of reef mean connection strength. Lighter colours indicate higher
RSD %
values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
fig-align="center" width="14.82cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
total connectivity strength and the number of years cover exceeds the carbonate budget
threshold. Colour of each point represents the base-10 log of scaled reef total connectivity
strength. Displays results from median timeseries using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
fig-align="center" width="14.82cm"}

@@

![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
clusters with the highest median area-relative cover between 2030 and 2040 within each
bioregion. Solid lines represent the cluster median timeseries and bands represent the 95th
percentile confidence intervals. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
fig-align="center" width="14.82cm"}

![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines represent the median cover – DHW correlation level for each cluster. Displays results
for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
fig-align="center" width="14.82cm"}

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW level for each cluster. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
fig-align="center" width="14.82cm"}

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
fig-align="center" width="14.82cm"}

![Initial proportion of coral habitable area occupied by corals for reefs within each
bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
are clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines represent the median proportion of habitable area occupied for each cluster. Displays
results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
fig-align="center" width="14.82cm"}

![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines within each violin represent the median source-to-sink ratio for each cluster and grey
points represent the ratio value for each reef. Vertical grey lines represent a
source-to-sink ratio of 0 (in base-10 log scale) indicating equal outgoing and incoming
connectivity levels. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
fig-align="center" width="14.82cm"}

![Total connectivity strength (in base-10 log scale) for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines within each violin represent the median base-10 log of total connectivity strength for
each cluster. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
fig-align="center" width="14.82cm"}
